RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-08 paper.tex
a few new references, much more needed

@@

Kandel's interview study points out the typical ``explore'',
``model'', ``report'' cycle~\cite{Kandel:2012:EDA}. There
are many discontinuities in this cycle that cost time and
effort to overcome.  RCloud seeks to reduce this impedance
mismatch. Kandel et al also point out that larger teams are
becoming more common in data analysis, that supporting
collaboration is a difficult and important problem, and that
sharing and versioning of data sources and artifacts is hindered
by current technology in practice. ``We found that analysts typically
did not share scripts with each other. Scripts that were shared were
disseminated similarly to intermediate data: either through shared
drives or email. Analysts rarely stored their analytic code in
source control.'' Their work points to the opportunity for better
technology to support collaboration and sharing by data analysis teams.

@@

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. iPython \cite{Perez:2007:ISI:1251563.1251831}
shares many of our goals...

@@

@@

>>>>

"Coordination is done by meetings"

"how do you trace an automated alert back to an EDA environment ?"

@@

Kandel et al. argue in their review of data wrangling work that data
cleaning, wrangling and transformation is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}. Although RCloud
does not by itself include modules specific to data cleaning and
wrangling, we note from internal experience that these cleaning
scripts themselves tend to change over time. RCloud addresses this
issue by providing easy publishing of data-cleaning notebooks as web
services, which reduces the total data-cleaning effort across an
organization.

Kandel et al.'s interview study points out the typical ``explore'',
``model'', ``report'' cycle in enterprise data
analysis~\cite{Kandel:2012:EDA}. There are many discontinuities in
this cycle that cost time and effort to overcome.  RCloud seeks to
reduce this impedance mismatch. They also point out that larger teams
are becoming more common in data analysis, that supporting
collaboration is a difficult and important problem, and that sharing
and versioning of data sources and artifacts is hindered by current
technology in practice. ``We found that analysts typically did not
share scripts with each other. Scripts that were shared were
disseminated similarly to intermediate data: either through shared
drives or email. Analysts rarely stored their analytic code in source
control.'' Their work points to the opportunity for better technology
to support collaboration and sharing by data analysis teams.

@@

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:ISI:1251563.1251831}
shares many of our goals...

@@

Notebooks as versioned subroutines, web services.

Notebooks by default are visible by the entire organization: there
exists a URL for every notebook in RCloud. This is deliberate. As
pointed out by Wattenberg and Kriss~\cite{Wattenberg:2011:DFS}, broad
access to analysis outputs (in their case, in the form of NameVoyager)
increases long-term engagement partly by the crossreferences in the
web. Our main RCloud deployment is only visible inside an intranet,
but we have nevertheless found anecdotal support for this theory by
noticing links to RCloud notebooks in internal discussion fora and
mailing lists.

@@

Asynchronous collaborative visual analytics
(ACVA)~\cite{Chen:2011:SEC}. This paper addresses visualization
\emph{of} the ACVA process. It will be important when we talk about
recommendation systems, and navigation of the set of notebooks, etc.
